\thetitle

### 2025-07-10 workshop/paper.tex
TPG section + reorder
new devels + fixes
NS commnets
replace PT appendix with nutshell section
finish
workshop submission file

\begin{icmlauthorlist}
\icmlauthor{Nikola Surjanovic}{ubc}
\icmlauthor{Miguel Biron-Lattes}{sfu}
\icmlauthor{Paul Tiede}{harvard}
\icmlauthor{Saifuddin Syed}{oxford}
\icmlauthor{Alexandre Bouchard-C{\^o}t{\'e}}{ubc}
\icmlauthor{Trevor Campbell}{ubc}
\end{icmlauthorlist}

\icmlaffiliation{harvard}{Center for Astrophysics, Harvard University, United States}
\icmlaffiliation{oxford}{Department of Statistics, University of Oxford, United Kingdom}
\icmlaffiliation{sfu}{Department of Statistics and Actuarial Sciences, Simon Fraser University, Canada}
\icmlaffiliation{ubc}{Department of Statistics, University of British Columbia, Canada}

@@

\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution

\input{abstract}
\input{introduction.tex}
\input{SPI.tex}
\input{related.tex}
%\input{conclusion.tex}
%\input{ack}

\bibliographystyle{icml2025}
\bibliography{../paper/ref.bib}

@@

\input{examples}
\input{PT}

>>>>

\begin{icmlauthorlist}
\icmlauthor{Miguel Biron-Lattes}{sfu}
\icmlauthor{Nikola Surjanovic}{ubc}
\icmlauthor{Paul Tiede}{harvard}
\icmlauthor{Saifuddin Syed}{oxford}
\icmlauthor{Trevor Campbell}{ubc}
\icmlauthor{Alexandre Bouchard-C{\^o}t{\'e}}{ubc}
\end{icmlauthorlist}

\icmlaffiliation{harvard}{Center for Astrophysics and Black Hole Initiative, Harvard University, United States}
\icmlaffiliation{oxford}{Department of Statistics, University of Oxford, United Kingdom}
\icmlaffiliation{sfu}{Department of Statistics and Actuarial Sciences, Simon Fraser University, Canada}
\icmlaffiliation{ubc}{Department of Statistics, University of British Columbia, Canada}

@@

\printAffiliationsAndNotice{
This is a summarized and revised version of \citet{surjanovic2025pigeons}.
}  % leave blank if no need to mention equal contribution

\input{abstract}
\input{introduction.tex}
\input{nutshell}
\input{overview}
\input{SPI.tex}
\input{new_developments}
%\input{related.tex}
\input{conclusion}
%\input{ack}

\bibliographystyle{icml2025}
\bibliography{../paper/ref.bib,ref.bib}

@@

\input{examples}
%\input{PT}
